Comparison among doublet predictions on benchmarking datasets

### 2024-06-26 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
small pca plot fix, but plots still not rendering?

      pc_color_columns <- c("scDblFInder prediction" = "scdbl_prediction",
                            "scublet prediction" = "scrublet_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")

@@

      patchwork::wrap_plots(pc_plot_list, pca_metrics) +
        plot_annotation(
            glue::glue("PCA for {dataset}"), 
            theme = theme(plot.title = element_text(size = 16))) + 
          plot_layout(guides = "collect") 
    }
  )
```

>>>>

      pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                            "scublet prediction" = "scrublet_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")

@@

      patchwork::wrap_plots(pc_plot_list) +
        plot_annotation(
            glue::glue("PCA for {dataset}"), 
            theme = theme(plot.title = element_text(size = 16))) + 
        plot_layout(guides = "collect")
    }
  )
```
